Yeast RNA-seq 48 sample simulation study

### 2018-03-13 datasets/RNA-Seq/yeast-simulation.Rmd
Add covariate line plot

covariateHeatmap(null5, alpha=0.05, covname="log2FC")
covariateHeatmap(null5, alpha=0.05, covname="ind_covariate")

@@

covariateHeatmap(null10, alpha=0.05, covname="log2FC")
covariateHeatmap(null10, alpha=0.05, covname="ind_covariate")

@@

covariateHeatmap(de5, alpha=0.05, covname="log2FC")
covariateHeatmap(de5, alpha=0.05, covname="ind_covariate")

@@

covariateHeatmap(de10, alpha=0.05, covname="log2FC")
covariateHeatmap(de10, alpha=0.05, covname="ind_covariate")

>>>>

covariateHeatmap(null5, alpha=0.05, covname="log2FC", trans="log1p")
covariateHeatmap(null5, alpha=0.05, covname="ind_covariate", trans="log1p")

covariateHeatmap(null5, alpha=0.05, covname="log2FC", nbins=25, 
                 trans="log1p", linePlot = TRUE)
covariateHeatmap(null5, alpha=0.05, covname="ind_covariate", nbins=25, 
                 linePlot = TRUE, trans="log1p")

@@

covariateHeatmap(null10, alpha=0.05, covname="log2FC", trans="log1p")
covariateHeatmap(null10, alpha=0.05, covname="ind_covariate", trans="log1p")

covariateHeatmap(null10, alpha=0.05, covname="log2FC", nbins=25, 
                 trans="log1p", linePlot = TRUE)
covariateHeatmap(null10, alpha=0.05, covname="ind_covariate", nbins=25, 
                 linePlot = TRUE, trans="log1p")

@@

covariateHeatmap(de5, alpha=0.05, covname="log2FC", trans="log1p")
covariateHeatmap(de5, alpha=0.05, covname="ind_covariate")

covariateHeatmap(de5, alpha=0.05, covname="log2FC", nbins=25, 
                 trans="log1p", linePlot = TRUE)
covariateHeatmap(de5, alpha=0.05, covname="ind_covariate", nbins=25, 
                 linePlot = TRUE)

@@

covariateHeatmap(de10, alpha=0.05, covname="log2FC", trans="log1p")
covariateHeatmap(de10, alpha=0.05, covname="ind_covariate")

covariateHeatmap(de10, alpha=0.05, covname="log2FC", nbins=25, 
                 trans="log1p", linePlot = TRUE)
covariateHeatmap(de10, alpha=0.05, covname="ind_covariate", nbins=25, 
                 linePlot = TRUE)
